\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-07-09 paper/eccv2020CR/sections/related.tex
Added eccv2020 camera-ready draft.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov
Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and
non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural
networks have been applied to this problem, \edit{for example using a multi-scale neural network to predict depth maps~\cite{Eigen2014},
using an unsupervised approach that trains a network using stereo pairs~\cite{Godard2017}, and using a logarithmic
depth discretization scheme combined with an ordinal regression loss function~\cite{Fu2018}}. Various
experiments using different types of encoder networks (\eg, ResNet,
DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some
success, as have approaches mixing deep learning with conditional random
fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of
monocular depth estimation using cross-dataset transfer.

Despite achieving remarkable success on estimating ordinal depth from a single
image, none of these methods is able to resolve inherent scale ambiguity in a
principled manner. We introduce a new approach that leverages existing monocular
depth estimation networks and disambiguates the output using depth
histogram--like measurements obtained from a single \edit{time-resolved detector}. Other
approaches to disambiguating monocular depth estimation use optimized freeform
lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel
sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors
and specialized image reconstruction methods. \edit{In contrast, our approach adds
minimal additional hardware to a single RGB camera, and may leverage sensors currently
deployed in consumer electronics.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Depth Imaging and Sensor Fusion with Time-resolved Detectors}
%
\edit{Emerging LiDAR systems use avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs)
to record the time of flight of individual photons. These time-resolved detectors} can be
fabricated using standard CMOS processes, but the required time-stamping electronics are challenging to miniaturize and fabricate at low
cost. For this reason, many \edit{LiDAR systems}, especially those using SPADs, use a single \edit{or a few detectors}
combined with a  scanning
mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single,gupta2019photonflooded}.
Unfortunately, this makes it challenging to scan dynamic scenes at high
resolution and scanners can also be expensive, difficult to calibrate, and prone
to mechanical failure. To reduce the scanning complexity to one dimension, \edit{1D
detector arrays} have been
developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of
research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet,
single-pixel \edit{time-resolved detectors} remain the only viable option for low-cost consumer devices
today.

The proposed method uses a single-pixel \edit{APD or SPAD} and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the \edit{transient} measurement with the
output of a monocular depth estimator using a histogram matching technique.
While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Histogram Matching and Global Hints}
%
Histogram matching is a well-known image processing technique for adjusting an
image so that its histogram matches some pre-specified histogram (often derived
from another image)~\cite{gonzales1977gray,Gonzalez2008}. Nikolova et
al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the
image pixels, yielding an exact histogram match. Morovic et
al.~\cite{Morovic2002} provide an efficient and precise method for fast
histogram matching which supports weighted pixel values. In the image
reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram
to form an image prior based on the Wasserstein distance for image denoising and
inpainting. Rother et al.~\cite{Rother2006} use a histogram prior to create an
energy function that penalizes foreground segmentations with dissimilar
histograms. \edit{Caramazza et al.~\cite{caramazza2018neural} use a single
non-line-of-sight transient to recover the identity of a person hidden from
view.} In a slightly different application area, Zhang et
al.~\cite{Zhang2017} train a neural network to produce realistically colorized
images given only a black-and-white image and a histogram of global color
information.

In our procedure, the \edit{transient measurements} closely resemble a histogram of
the depth map where the histogram values are weighted by spatially varying scene
reflectances and inverse-square falloff effects. We therefore adapt the
algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general
per-pixel weights during histogram matching.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov
Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and
non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural
networks have been applied to this problem, for example using a multi-scale neural network to predict depth maps~\cite{Eigen2014},
using an unsupervised approach that trains a network using stereo pairs~\cite{Godard2017}, and using a logarithmic
depth discretization scheme combined with an ordinal regression loss function~\cite{Fu2018}. Various
experiments using different types of encoder networks (\eg, ResNet,
DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some
success, as have approaches mixing deep learning with conditional random
fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of
monocular depth estimation using cross-dataset transfer.

Despite achieving remarkable success on estimating ordinal depth from a single
image, none of these methods is able to resolve inherent scale ambiguity in a
principled manner. We introduce a new approach that leverages existing monocular
depth estimation networks and disambiguates the output using depth
histogram--like measurements obtained from a single time-resolved detector. Other
approaches to disambiguating monocular depth estimation use optimized freeform
lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel
sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors
and specialized image reconstruction methods. In contrast, our approach adds
minimal additional hardware to a single RGB camera, and may leverage sensors currently
deployed in consumer electronics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Depth Imaging and Sensor Fusion with Time-resolved Detectors}
%
Emerging LiDAR systems use avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs)
to record the time of flight of individual photons. These time-resolved detectors can be
fabricated using standard CMOS processes, but the required time-stamping electronics are challenging to miniaturize and fabricate at low
cost. For this reason, many LiDAR systems, especially those using SPADs, use a single or a few detectors
combined with a  scanning
mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single,gupta2019photonflooded}.
Unfortunately, this makes it challenging to scan dynamic scenes at high
resolution and scanners can also be expensive, difficult to calibrate, and prone
to mechanical failure. To reduce the scanning complexity to one dimension, 1D
detector arrays have been
developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of
research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet,
single-pixel time-resolved detectors remain the only viable option for low-cost consumer devices
today.

The proposed method uses a single-pixel APD or SPAD and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the transient measurement with the
output of a monocular depth estimator using a histogram matching technique.
While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Histogram Matching and Global Hints}
%
Histogram matching is a well-known image processing technique for adjusting an
image so that its histogram matches some pre-specified histogram (often derived
from another image)~\cite{gonzales1977gray,Gonzalez2008}. Nikolova et
al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the
image pixels, yielding an exact histogram match. Morovic et
al.~\cite{Morovic2002} provide an efficient and precise method for fast
histogram matching which supports weighted pixel values. In the image
reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram
to form an image prior based on the Wasserstein distance for image denoising and
inpainting. Rother et al.~\cite{Rother2006} use a histogram prior to create an
energy function that penalizes foreground segmentations with dissimilar
histograms. Caramazza et al.~\cite{caramazza2018neural} use a single
non-line-of-sight transient to recover the identity of a person hidden from
view. In a slightly different application area, Zhang et
al.~\cite{Zhang2017} train a neural network to produce realistically colorized
images given only a black-and-white image and a histogram of global color
information.

In our procedure, the transient measurements closely resemble a histogram of
the depth map where the histogram values are weighted by spatially varying scene
reflectances and inverse-square falloff effects. We therefore adapt the
algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general
per-pixel weights during histogram matching.

### 2020-07-09 paper/eccv2020CR/sections/simulation.tex
Added eccv2020 camera-ready draft.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation Details}

@@

To simulate a \edit{transient}, we take the provided depth map and 
calculate a weighted depth histogram by weighting the pixel contributions to
each depth bin by the luminance of each pixel. To model radiometric falloff, we
multiply each bin by $1/z^2$, and convolve with a modeled system temporal
response, which we approximate as a Gaussian with a full-width at half-maximum of 70~ps. We scale
the histogram by the total number of observed signal photon counts (set to 
$10^6$) and  add a fixed number of background photons $b \in \set{2\times 10^5, 10^5, 2\times
10^4, 10^4}$. The background counts are evenly distributed across all bins to simulate the ambient and dark
count detections, and the different background levels correspond to
signal-to-background ratios (SBR) of $5, 10, 50$ and $100$ respectively. Finally,
each bin is Poisson sampled to produce the final simulated transient.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Results}
\begin{table*}[!t]
  \begin{center}
   {\fontsize{7pt}{8pt}\selectfont 
      \input{sections/figures/sim_table.tex}
   } 
\caption{
  Quantitative evaluation using NYU Depth v2. Bold indicates best
performance for that metric, while underline indicates second best. The proposed
scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or
even outperforms the median rescaling scheme and histogram matching with the
exact depth map histogram, even though those methods have access to ground
truth.}
\label{tab:comparison}
\end{center}
\end{table*}

@@

Instead, our method uses the simulated measurements from a single \edit{aggregated transient} to correct the depth map. In Table~\ref{tab:comparison}, results are shown for several different
signal-to-background ratios (SBRs). We see that the proposed method achieves
high-quality results for correcting the raw depth map estimated by the
respective CNNs for all cases. The quality of the resulting depth maps is almost
as good as that achieved with the oracle ground truth histogram, which can be
interpreted as an approximate upper bound on the performance, despite a
relatively high amount of noise and background signal. These results demonstrate
that the proposed method is agnostic to the specific depth estimation CNN
applied to get the initial depth map and that it generally achieves significant
improvements in the estimated depth maps, clearly surpassing the variation in
performance between depth estimation CNNs.

\begin{figure*}[t]
  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
  \includegraphics[width=\textwidth]{comparison.pdf}
  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
  \caption{Simulated results from NYU Depth v2 computed with the DenseDepth
  CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
  but contain systematic error. Oracle access to the ground truth depth maps,
  either through the median depth or the depth histogram, can remove this error
  and correct the depth maps. \edit{The proposed method uses a single transient measurement} and does not rely on ground truth depth, but it achieves
  a quality that closely matches the best-performing oracle.}
	\label{fig:results_simulated}
  \vspace{-1em}
\end{figure*}

In Figure~\ref{fig:results_simulated}, we also show qualitative results of our
simulations. For each of these scenes, we show the RGB reference image, the
ground truth depth map, the raw output of the DenseDepth CNN, the result of
rescaling the CNN output with the median ground truth depth, the result of
histogram-matching the CNN output by the ground truth depth map histogram, and
the result achieved by the proposed method for an SBR of 100. Error maps for all
the depth estimation methods are shown. As expected, the CNN outputs depth maps
that look reasonable but that have an average root mean squared error (RMSE) of
about 50--60~cm. Rescaling this depth map to match the median ground truth depth
value slightly improves the quality and histogram-matching with the ground
truth depth histogram shows a large amount of improvement. The quality of the
proposed method is close to using the oracle histogram, despite relying on
noisy \edit{transient} measurements. Additional simulations using DenseDepth and other depth
estimation CNNs for a variety of scenes are shown in the supplement.

>>>>

\subsection{Implementation Details}

@@

To simulate a transient, we take the provided depth map and calculate a weighted
depth histogram by weighting the pixel contributions to each depth bin by the
luminance of each pixel. To model radiometric falloff, we multiply each bin by
$1/z^2$, and convolve with a modeled system temporal response, which we
approximate as a Gaussian with a full-width at half-maximum of 70~ps. We scale
the histogram by the total number of observed signal photon counts (set to
$10^6$) and  add a fixed number of background photons
$b \in \set{2\times 10^5, 10^5, 2\times 10^4, 10^4}$. The background counts are
evenly distributed across all bins to simulate the ambient and dark count
detections, and the different background levels correspond to
signal-to-background ratios (SBR) of $5, 10, 50$ and $100$ respectively.
Finally, each bin is Poisson sampled to produce the final simulated transient.

\subsection{Simulated Results}
\begin{table*}[!t]
  \begin{center}
      \input{sections/figures/sim_table.tex}
\caption{
  Quantitative evaluation using NYU Depth v2. Bold indicates best
performance for that metric, while underline indicates second best. The proposed
scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or
even outperforms the median rescaling scheme and histogram matching with the
exact depth map histogram, even though those methods have access to ground
truth. \edit{Metric definitions can be found in~\cite{Eigen2014}.}}
\label{tab:comparison}
\end{center}
\end{table*}

@@

Instead, our method uses the simulated measurements from a single aggregated
transient to correct the depth map. In Table~\ref{tab:comparison}, results are
shown for several different signal-to-background ratios (SBRs). We see that the
proposed method achieves high-quality results for correcting the raw depth map
estimated by the respective CNNs for all cases. The quality of the resulting
depth maps is almost as good as that achieved with the oracle ground truth
histogram, which can be interpreted as an approximate upper bound on the
performance, despite a relatively high amount of noise and background signal.
These results demonstrate that the proposed method is agnostic to the specific
depth estimation CNN applied to get the initial depth map and that it generally
achieves significant improvements in the estimated depth maps, clearly
surpassing the variation in performance between depth estimation CNNs.

\begin{figure*}[t]
  \includegraphics[width=\textwidth]{comparison.pdf}
  \caption{Simulated results from NYU Depth v2 computed with the DenseDepth
    CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
    but contain systematic error. Oracle access to the ground truth depth maps,
    either through the median depth or the depth histogram, can remove this
    error and correct the depth maps. The proposed method uses a single
    transient measurement and does not rely on ground truth depth, but it
    achieves a quality that closely matches the best-performing oracle.}
	\label{fig:results_simulated}
\end{figure*}

In Figure~\ref{fig:results_simulated}, we also show qualitative results of our
simulations. For each of these scenes, we show the RGB reference image, the
ground truth depth map, the raw output of the DenseDepth CNN, the result of
rescaling the CNN output with the median ground truth depth, the result of
histogram-matching the CNN output by the ground truth depth map histogram, and
the result achieved by the proposed method for an SBR of 100. Error maps for all
the depth estimation methods are shown. As expected, the CNN outputs depth maps
that look reasonable but that have an average root mean squared error (RMSE) of
about 50--60~cm. Rescaling this depth map to match the median ground truth depth
value slightly improves the quality and histogram-matching with the ground
truth depth histogram shows a large amount of improvement. The quality of the
proposed method is close to using the oracle histogram, despite relying on
noisy transient measurements. Additional simulations using DenseDepth and other
depth estimation CNNs for a variety of scenes are shown in the supplement.

### 2020-07-09 paper/eccv2020CR/supplement.tex
Added eccv2020 camera-ready draft.

% CAMERA READY SUBMISSION
\begin{comment}
\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
\end{comment}
%******************
\maketitle

@@

\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
  \caption{Comparison of scan + sum and diffused SPAD. The transients are captured
      with the same total exposure time and are qualitatively similar without 
      noticeable pileup effects.}
  \label{fig:comparison}
\end{figure}

@@

\section{Nominal values for SBR calculation}
Here we give the values used in the equation for received power, repeated here
for convenience:
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
  \end{equation}
The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    Symbol & Description & Nominal Value \\
    \midrule
    $\rho$  & Albedo of lambertian surface & $0.3$ \\
    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
    $R$ & Distance to surface (m) & $3$ \\
    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
    $\eta$ & Quantum efficiency of detector & $0.3$ \\
    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
    \bottomrule
  \end{tabular}
  \caption{}
  \label{fig:sbr_calculation}
\end{figure}
Once $P_R$ is determined, we compute the number of photons using the laser
wavelength $\lambda = 532$ nm as
\begin{equation}
  N = \frac{P_R\lambda}{hc}
\end{equation}
where $h \approx 6.626 \times 10^{-34}$ is Planck's constant and $c \approx 3
\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
MHz, we get the number of photons per pulse as $0.043$, which puts us in the
low-flux regime.

@@

\section{Ablation study on effect of reflectance estimation}
We conducted an ablation study on whether the use of a reflectance
estimate has an impact on the runtime and quality of the solution.
We performed this analysis using SPAD
data with a signal-to-background (SBR) of 100, simulated on the test set of NYU
Depth v2 and using DenseDepth~\cite{Alhashim2018} for our MDE CNN.
Only the histogram matching portion was timed, not the CNN nor the denoising pipeline.

>>>>

% CAMERA READY SUBMISSION
\begin{comment}
\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
\end{comment}
%******************
\maketitle
\begin{abstract}
  TODO: Abstract
\end{abstract}

@@

\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
  \caption{Comparison of scan + sum and diffused SPAD. The transients are captured
      with the same total exposure time and are qualitatively similar without 
      noticeable pileup effects. We Use $K = 300$ bins for the reconstruction
      and a depth range of $[0.8, 6]$ meters. MiDaS \cite{Lasinger:2019} does
      not produce globally-scaled depth, so we scale it to fit this depth range.
      We inpaint the depth map from the Kinect's depth camera to acquire ground
      truth depth.}
  \label{fig:comparison}
\end{figure}

@@

\section{Nominal values for radiometric calculation}
Here we give the values used in the equation for received power, repeated here
for convenience:
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
  \end{equation}
  For our scene, we assume a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    Symbol & Description & Nominal Value \\
    \midrule
    $\rho$  & Albedo of lambertian surface & $0.3$ \\
    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
    $R$ & Distance to surface (m) & $3$ \\
    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
    $\eta$ & Quantum efficiency of detector & $0.3$ \\
    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
    \bottomrule
  \end{tabular}
  \caption{Table of nominal values for radiometric calculation.}
  \label{fig:sbr_calculation}
\end{figure}
Once $P_R$ is determined, we compute the number of photons using the laser
wavelength $\lambda = 532$ nm as
\begin{equation}
  N = \frac{P_R\lambda}{hc}
\end{equation}
where $h \approx 6.626 \times 10^{-34}$ $\text{J} \cdot \text{s}$ is Planck's constant and $c \approx 3
\times 10^8$ $\text{m}/\text{s}$ is the speed of light. Using the fact that our laser runs at 10
MHz, we get the number of photons per pulse as $0.043$ or $4.3\%$, which puts us in the
low-flux regime (where photons per pulse is $< 5\%$).

@@

\section{Ablation study on effect of reflectance estimation}
We conducted an ablation study on whether the use of a reflectance
estimate has an impact on the runtime and quality of the solution.
We performed this analysis using SPAD
data with a signal-to-background (SBR) of 100, simulated on the test set of NYU
Depth v2 and using DenseDepth~\cite{Alhashim2018} for our MDE CNN.
Only the histogram matching portion was timed, not the CNN nor the denoising
pipeline. Using the intensity to produce the initial weighted histogram
$h_{\text{source}} $ provides noticable improvements
in RMSE, but intensity may safely be ignored during the pixel movement step,
resulting in noticeable speed improvements.
